\subsection{GlobalVariables}
\label{GlobalVariables}
Allows to access contents of \texttt{GVars.dbf}.
\subsubsection{Properties}
\begin{center}
\begin{tabularx}{\linewidth}{| l | X |}
\hline
\textbf{Name} & \textbf{Description}\\
\hline
weapnMstr & Instructor skill bonus experience, \texttt{WEAPN\_MSTR}\\
\hline
batInit & Max additional initiative points that randomly added to unit in battle. \texttt{BAT\_INIT}\\
\hline
batDamage & Max additional damage points that randomly added to unit damage in battle. \texttt{BAT\_DAMAGE}\\
\hline
batRound & \texttt{BAT\_ROUND}\\
\hline
batBreak & \texttt{BAT\_BREAK}\\
\hline
batBModif & \texttt{BAT\_BMODIF}\\
\hline
batLoweri & Initiative debuff. \texttt{BATLOWERI}\\
\hline
ldrMaxAbil & Maximum number of abilities leader can learn. \texttt{LDRMAXABIL}\\
\hline
spyDiscov & Spy discovery chance per turn. \texttt{SPY\_DISCOV}\\
\hline
poisonC & Damage from thief action 'poison city'. \texttt{POISON\_C}\\
\hline
poisonS & Damage from thief action 'poison stack'. \texttt{POISON\_S}\\
\hline
bribe & Bribe multiplier. \texttt{BRIBE}\\
\hline
stealRace & \texttt{STEAL\_RACE}\\
\hline
stealNeut & \texttt{STEAL\_NEUT}\\
\hline
riotMin & Minimal riot duration in days. \texttt{RIOT\_MIN}\\
\hline
riotMax & Maximal riot duration in days. \texttt{RIOT\_MAX}\\
\hline
riotDmg & Percentage of riot damage. \texttt{RIOT\_DMG}\\
\hline
sellRatio & Percentage of the original price of the items at sale. \texttt{SELL\_RATIO}\\
\hline
tCapture & Land transformation after city capture. \texttt{T\_CAPTURE}\\
\hline
tCapital & Land transformation per turn by capital. \texttt{T\_CAPITAL}\\
\hline
rodRange & Range of land transformation by rod per turn. \texttt{ROD\_RANGE}\\
\hline
crystalP & Profit per mana crystal or gold mine per turn. \texttt{CRYSTAL\_P}\\
\hline
constUrg & \texttt{CONST\_URG}\\
\hline
regenLwar & Bonus per day regeneration for fighter leader. \texttt{REGEN\_LWAR}\\
\hline
regenRuin & Bonus per day regeneration for units in ruins. \texttt{REGEN\_RUIN}\\
\hline
dPeace & Diplomacy level representing peace. \texttt{D\_PEACE}\\
\hline
dWar & Diplomacy level representing war. \texttt{D\_WAR}\\
\hline
dNeutral & Diplomacy level representing neutrality. \texttt{D\_NEUTRAL}\\
\hline
dGold & \texttt{D\_GOLD}\\
\hline
dMkAlly & \texttt{D\_MK\_ALLY}\\
\hline
dAttakSc & \texttt{D\_ATTACK\_SC}\\
\hline
dAttakFo & \texttt{D\_ATTACK\_FO}\\
\hline
dAttakPc & \texttt{D\_ATTACK\_PC}\\
\hline
dRod & \texttt{D\_ROD}\\
\hline
dRefAlly & \texttt{D\_REF\_ALLY}\\
\hline
dBkAlly & \texttt{D\_BK\_ALLY}\\
\hline
dNoble & \texttt{D\_NOBLE}\\
\hline
dBkaChnc & \texttt{D\_BKA\_CHANCE}\\
\hline
dBkaTurn & \texttt{D\_BKA\_TURN}\\
\hline
\end{tabularx}
\end{center}
\begin{center}
\begin{tabularx}{\linewidth}{| l | X |}
\hline
\textbf{Name} & \textbf{Description}\\
\hline
protCap & Capital protection. \texttt{PROT\_CAP}\\
\hline
bonusE & Additional gold on easy difficulty. \texttt{BONUS\_E}\\
\hline
bonusA & Additional gold on average difficulty. \texttt{BONUS\_A}\\
\hline
bonusH & Additional gold on hard difficulty. \texttt{BONUS\_H}\\
\hline
bonusV & Additional gold on very hard difficulty. \texttt{BONUS\_V}\\
\hline
incomeE & Income increase on easy difficulty. \texttt{INCOME\_E}\\
\hline
incomeA & Income increase on average difficulty. \texttt{INCOME\_A}\\
\hline
incomeH & Income increase on hard difficulty. \texttt{INCOME\_H}\\
\hline
incomeV & Income increase on very hard difficulty. \texttt{INCOME\_V}\\
\hline
guRange & \texttt{GU\_RANGE}\\
\hline
paRange & \texttt{PA\_RANGE}\\
\hline
loRange & \texttt{LO\_RANGE}\\
\hline
defendBonus & Armor bonus when unit uses defend in battle. \texttt{DFENDBONUS}\\
\hline
talisChrg & \texttt{TALIS\_CHRG}\\
\hline
gainSpell & Chance to get spells with capture of a capital. \texttt{GAIN\_SPELL}\\
\hline
rodCost & Rod placement cost. \texttt{ROD\_COST}\\
\hline
\end{tabularx}
\end{center}
\subsubsection{Methods}
\begin{center}
\begin{tabularx}{\linewidth}{| l | X |}
\hline
\textbf{Name} & \textbf{Description}\\
\hline
morale(n) & Input tier values must be in range \texttt{[1 : 6]}. \texttt{MORALE\_n}\\
\hline
batBoostd(n) & Damage boost values for various levels. Levels must be in range \texttt{[1 : 4]}. \texttt{BATBOOSTDn}\\
\hline
batLowerd(n) & Damage debuff values for various levels. Levels must be in range \texttt{[1 : 2]}. \texttt{BATLOWERDn}\\
\hline
tCity(n) & Land transformation per turn by cities of different tiers. Tier must be in range \texttt{[1 : 5]}. \texttt{T\_CITYn}\\
\hline
prot(n) & City protection values for various tier levels. Tier must be in range \texttt{[1 : 6]}. In case of tier 6, returns \texttt{protCap}. \texttt{PROT\_n}\\
\hline
splPwr(n) & Input tier values must be in range \texttt{[1 : 5]}. \texttt{SPLPWR\_n}\\
\hline
\end{tabularx}
\end{center}